---
title: "OUP Usage Across the UT System"
author: "Alexander Harriman"
date: "2024-12-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning = FALSE}
library(dplyr)
library(tidyverse)
library(gt)
library(stringr)
library(readxl)
library(ggplot2)
library(ggthemes)
library(janitor)
library(writexl)
```


# Load Data - UT Chattanooga


### TR_J1

```{r}
utcTR_J1 <- read.csv('report_tr_j1_2022-01-2024-12.csv', skip = 13) |>
  mutate(Location = 'UT Chattanooga',
         Total_Usage = Reporting_Period_Total) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan.2022`) == FALSE, `Jan.2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb.2022`) == FALSE, `Feb.2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar.2022`) == FALSE, `Mar.2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr.2022`) == FALSE, `Apr.2022`, 0),
         `May-2022` = ifelse(is.na(`May.2022`) == FALSE, `May.2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun.2022`) == FALSE, `Jun.2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul.2022`) == FALSE, `Jul.2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug.2022`) == FALSE, `Aug.2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep.2022`) == FALSE, `Sep.2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct.2022`) == FALSE, `Oct.2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov.2022`) == FALSE, `Nov.2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec.2022`) == FALSE, `Dec.2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan.2023`) == FALSE, `Jan.2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb.2023`) == FALSE, `Feb.2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar.2023`) == FALSE, `Mar.2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr.2023`) == FALSE, `Apr.2023`, 0),
         `May-2023` = ifelse(is.na(`May.2023`) == FALSE, `May.2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun.2023`) == FALSE, `Jun.2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul.2023`) == FALSE, `Jul.2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug.2023`) == FALSE, `Aug.2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep.2023`) == FALSE, `Sep.2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct.2023`) == FALSE, `Oct.2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov.2023`) == FALSE, `Nov.2023`, 0),
         `Dec-2023` = ifelse(is.na(`Dec.2023`) == FALSE, `Dec.2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan.2024`) == FALSE, `Jan.2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb.2024`) == FALSE, `Feb.2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar.2024`) == FALSE, `Mar.2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr.2024`) == FALSE, `Apr.2024`, 0),
         `May-2024` = ifelse(is.na(`May.2024`) == FALSE, `May.2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun.2024`) == FALSE, `Jun.2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul.2024`) == FALSE, `Jul.2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug.2024`) == FALSE, `Aug.2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep.2024`) == FALSE, `Sep.2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct.2024`) == FALSE, `Oct.2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov.2024`) == FALSE, `Nov.2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec.2024`) == FALSE, `Dec.2024`, 0)) |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`)

utcTR_J1
```




### TR_J2

```{r}
utcTR_J2 <- read.csv('report_tr_j2_2022-01-2024-12.csv', skip = 13) |>
  mutate(Location = 'UT Chattanooga',
         Total_Usage = Reporting_Period_Total) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan.2022`) == FALSE, `Jan.2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb.2022`) == FALSE, `Feb.2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar.2022`) == FALSE, `Mar.2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr.2022`) == FALSE, `Apr.2022`, 0),
         `May-2022` = ifelse(is.na(`May.2022`) == FALSE, `May.2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun.2022`) == FALSE, `Jun.2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul.2022`) == FALSE, `Jul.2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug.2022`) == FALSE, `Aug.2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep.2022`) == FALSE, `Sep.2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct.2022`) == FALSE, `Oct.2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov.2022`) == FALSE, `Nov.2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec.2022`) == FALSE, `Dec.2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan.2023`) == FALSE, `Jan.2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb.2023`) == FALSE, `Feb.2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar.2023`) == FALSE, `Mar.2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr.2023`) == FALSE, `Apr.2023`, 0),
         `May-2023` = ifelse(is.na(`May.2023`) == FALSE, `May.2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun.2023`) == FALSE, `Jun.2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul.2023`) == FALSE, `Jul.2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug.2023`) == FALSE, `Aug.2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep.2023`) == FALSE, `Sep.2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct.2023`) == FALSE, `Oct.2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov.2023`) == FALSE, `Nov.2023`, 0),
         `Dec-2023` = ifelse(is.na(`Dec.2023`) == FALSE, `Dec.2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan.2024`) == FALSE, `Jan.2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb.2024`) == FALSE, `Feb.2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar.2024`) == FALSE, `Mar.2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr.2024`) == FALSE, `Apr.2024`, 0),
         `May-2024` = ifelse(is.na(`May.2024`) == FALSE, `May.2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun.2024`) == FALSE, `Jun.2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul.2024`) == FALSE, `Jul.2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug.2024`) == FALSE, `Aug.2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep.2024`) == FALSE, `Sep.2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct.2024`) == FALSE, `Oct.2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov.2024`) == FALSE, `Nov.2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec.2024`) == FALSE, `Dec.2024`, 0)) |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`)

utcTR_J2
```



### TR_J3

```{r}
utcTR_J3 <- read.csv('report_tr_j3_2022-01-2024-12.csv', skip = 13) |>
  mutate(Location = 'UT Chattanooga',
         Total_Usage = Reporting_Period_Total) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan.2022`) == FALSE, `Jan.2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb.2022`) == FALSE, `Feb.2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar.2022`) == FALSE, `Mar.2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr.2022`) == FALSE, `Apr.2022`, 0),
         `May-2022` = ifelse(is.na(`May.2022`) == FALSE, `May.2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun.2022`) == FALSE, `Jun.2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul.2022`) == FALSE, `Jul.2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug.2022`) == FALSE, `Aug.2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep.2022`) == FALSE, `Sep.2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct.2022`) == FALSE, `Oct.2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov.2022`) == FALSE, `Nov.2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec.2022`) == FALSE, `Dec.2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan.2023`) == FALSE, `Jan.2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb.2023`) == FALSE, `Feb.2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar.2023`) == FALSE, `Mar.2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr.2023`) == FALSE, `Apr.2023`, 0),
         `May-2023` = ifelse(is.na(`May.2023`) == FALSE, `May.2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun.2023`) == FALSE, `Jun.2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul.2023`) == FALSE, `Jul.2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug.2023`) == FALSE, `Aug.2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep.2023`) == FALSE, `Sep.2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct.2023`) == FALSE, `Oct.2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov.2023`) == FALSE, `Nov.2023`, 0),
         `Dec-2023` = ifelse(is.na(`Dec.2023`) == FALSE, `Dec.2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan.2024`) == FALSE, `Jan.2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb.2024`) == FALSE, `Feb.2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar.2024`) == FALSE, `Mar.2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr.2024`) == FALSE, `Apr.2024`, 0),
         `May-2024` = ifelse(is.na(`May.2024`) == FALSE, `May.2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun.2024`) == FALSE, `Jun.2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul.2024`) == FALSE, `Jul.2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug.2024`) == FALSE, `Aug.2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep.2024`) == FALSE, `Sep.2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct.2024`) == FALSE, `Oct.2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov.2024`) == FALSE, `Nov.2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec.2024`) == FALSE, `Dec.2024`, 0)) |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Access_Type, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`)

utcTR_J3
```



### TR_J4

```{r}
utcTR_J4 <- read.csv('report_tr_j4_2022-01-2024-12.csv', skip = 13) |>
  mutate(Location = 'UT Chattanooga',
         Total_Usage = Reporting_Period_Total) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan.2022`) == FALSE, `Jan.2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb.2022`) == FALSE, `Feb.2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar.2022`) == FALSE, `Mar.2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr.2022`) == FALSE, `Apr.2022`, 0),
         `May-2022` = ifelse(is.na(`May.2022`) == FALSE, `May.2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun.2022`) == FALSE, `Jun.2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul.2022`) == FALSE, `Jul.2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug.2022`) == FALSE, `Aug.2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep.2022`) == FALSE, `Sep.2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct.2022`) == FALSE, `Oct.2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov.2022`) == FALSE, `Nov.2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec.2022`) == FALSE, `Dec.2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan.2023`) == FALSE, `Jan.2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb.2023`) == FALSE, `Feb.2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar.2023`) == FALSE, `Mar.2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr.2023`) == FALSE, `Apr.2023`, 0),
         `May-2023` = ifelse(is.na(`May.2023`) == FALSE, `May.2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun.2023`) == FALSE, `Jun.2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul.2023`) == FALSE, `Jul.2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug.2023`) == FALSE, `Aug.2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep.2023`) == FALSE, `Sep.2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct.2023`) == FALSE, `Oct.2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov.2023`) == FALSE, `Nov.2023`, 0),
         `Dec-2023` = ifelse(is.na(`Dec.2023`) == FALSE, `Dec.2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan.2024`) == FALSE, `Jan.2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb.2024`) == FALSE, `Feb.2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar.2024`) == FALSE, `Mar.2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr.2024`) == FALSE, `Apr.2024`, 0),
         `May-2024` = ifelse(is.na(`May.2024`) == FALSE, `May.2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun.2024`) == FALSE, `Jun.2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul.2024`) == FALSE, `Jul.2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug.2024`) == FALSE, `Aug.2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep.2024`) == FALSE, `Sep.2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct.2024`) == FALSE, `Oct.2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov.2024`) == FALSE, `Nov.2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec.2024`) == FALSE, `Dec.2024`, 0)) |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, YOP, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`)

utcTR_J4
```





# Load Data - UT Health Science Center


### TR_J1

```{r}
uthscTR_J1 <- read.csv('UTHSC_report_tr_j1_2022-01-2024-12.csv', skip = 13) |>
  mutate(Location = 'Health Sciences',
         Total_Usage = Reporting_Period_Total) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan.2022`) == FALSE, `Jan.2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb.2022`) == FALSE, `Feb.2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar.2022`) == FALSE, `Mar.2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr.2022`) == FALSE, `Apr.2022`, 0),
         `May-2022` = ifelse(is.na(`May.2022`) == FALSE, `May.2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun.2022`) == FALSE, `Jun.2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul.2022`) == FALSE, `Jul.2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug.2022`) == FALSE, `Aug.2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep.2022`) == FALSE, `Sep.2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct.2022`) == FALSE, `Oct.2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov.2022`) == FALSE, `Nov.2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec.2022`) == FALSE, `Dec.2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan.2023`) == FALSE, `Jan.2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb.2023`) == FALSE, `Feb.2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar.2023`) == FALSE, `Mar.2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr.2023`) == FALSE, `Apr.2023`, 0),
         `May-2023` = ifelse(is.na(`May.2023`) == FALSE, `May.2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun.2023`) == FALSE, `Jun.2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul.2023`) == FALSE, `Jul.2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug.2023`) == FALSE, `Aug.2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep.2023`) == FALSE, `Sep.2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct.2023`) == FALSE, `Oct.2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov.2023`) == FALSE, `Nov.2023`, 0),
         `Dec-2023` = ifelse(is.na(`Dec.2023`) == FALSE, `Dec.2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan.2024`) == FALSE, `Jan.2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb.2024`) == FALSE, `Feb.2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar.2024`) == FALSE, `Mar.2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr.2024`) == FALSE, `Apr.2024`, 0),
         `May-2024` = ifelse(is.na(`May.2024`) == FALSE, `May.2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun.2024`) == FALSE, `Jun.2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul.2024`) == FALSE, `Jul.2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug.2024`) == FALSE, `Aug.2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep.2024`) == FALSE, `Sep.2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct.2024`) == FALSE, `Oct.2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov.2024`) == FALSE, `Nov.2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec.2024`) == FALSE, `Dec.2024`, 0)) |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`)

uthscTR_J1
```


### TR_J2

```{r}
uthscTR_J2 <- read.csv('UTHSC_report_tr_j2_2022-01-2024-12.csv', skip = 13) |>
  mutate(Location = 'Health Sciences',
         Total_Usage = Reporting_Period_Total) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan.2022`) == FALSE, `Jan.2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb.2022`) == FALSE, `Feb.2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar.2022`) == FALSE, `Mar.2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr.2022`) == FALSE, `Apr.2022`, 0),
         `May-2022` = ifelse(is.na(`May.2022`) == FALSE, `May.2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun.2022`) == FALSE, `Jun.2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul.2022`) == FALSE, `Jul.2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug.2022`) == FALSE, `Aug.2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep.2022`) == FALSE, `Sep.2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct.2022`) == FALSE, `Oct.2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov.2022`) == FALSE, `Nov.2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec.2022`) == FALSE, `Dec.2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan.2023`) == FALSE, `Jan.2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb.2023`) == FALSE, `Feb.2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar.2023`) == FALSE, `Mar.2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr.2023`) == FALSE, `Apr.2023`, 0),
         `May-2023` = ifelse(is.na(`May.2023`) == FALSE, `May.2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun.2023`) == FALSE, `Jun.2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul.2023`) == FALSE, `Jul.2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug.2023`) == FALSE, `Aug.2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep.2023`) == FALSE, `Sep.2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct.2023`) == FALSE, `Oct.2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov.2023`) == FALSE, `Nov.2023`, 0),
         `Dec-2023` = ifelse(is.na(`Dec.2023`) == FALSE, `Dec.2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan.2024`) == FALSE, `Jan.2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb.2024`) == FALSE, `Feb.2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar.2024`) == FALSE, `Mar.2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr.2024`) == FALSE, `Apr.2024`, 0),
         `May-2024` = ifelse(is.na(`May.2024`) == FALSE, `May.2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun.2024`) == FALSE, `Jun.2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul.2024`) == FALSE, `Jul.2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug.2024`) == FALSE, `Aug.2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep.2024`) == FALSE, `Sep.2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct.2024`) == FALSE, `Oct.2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov.2024`) == FALSE, `Nov.2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec.2024`) == FALSE, `Dec.2024`, 0)) |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`)

uthscTR_J2
```



### TR_J3

```{r}
uthscTR_J3 <- read.csv('UTHSC_report_tr_j3_2022-01-2024-12.csv', skip = 13) |>
  mutate(Location = 'Health Sciences',
         Total_Usage = Reporting_Period_Total) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan.2022`) == FALSE, `Jan.2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb.2022`) == FALSE, `Feb.2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar.2022`) == FALSE, `Mar.2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr.2022`) == FALSE, `Apr.2022`, 0),
         `May-2022` = ifelse(is.na(`May.2022`) == FALSE, `May.2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun.2022`) == FALSE, `Jun.2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul.2022`) == FALSE, `Jul.2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug.2022`) == FALSE, `Aug.2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep.2022`) == FALSE, `Sep.2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct.2022`) == FALSE, `Oct.2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov.2022`) == FALSE, `Nov.2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec.2022`) == FALSE, `Dec.2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan.2023`) == FALSE, `Jan.2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb.2023`) == FALSE, `Feb.2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar.2023`) == FALSE, `Mar.2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr.2023`) == FALSE, `Apr.2023`, 0),
         `May-2023` = ifelse(is.na(`May.2023`) == FALSE, `May.2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun.2023`) == FALSE, `Jun.2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul.2023`) == FALSE, `Jul.2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug.2023`) == FALSE, `Aug.2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep.2023`) == FALSE, `Sep.2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct.2023`) == FALSE, `Oct.2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov.2023`) == FALSE, `Nov.2023`, 0),
         `Dec-2023` = ifelse(is.na(`Dec.2023`) == FALSE, `Dec.2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan.2024`) == FALSE, `Jan.2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb.2024`) == FALSE, `Feb.2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar.2024`) == FALSE, `Mar.2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr.2024`) == FALSE, `Apr.2024`, 0),
         `May-2024` = ifelse(is.na(`May.2024`) == FALSE, `May.2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun.2024`) == FALSE, `Jun.2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul.2024`) == FALSE, `Jul.2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug.2024`) == FALSE, `Aug.2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep.2024`) == FALSE, `Sep.2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct.2024`) == FALSE, `Oct.2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov.2024`) == FALSE, `Nov.2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec.2024`) == FALSE, `Dec.2024`, 0)) |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Access_Type, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`)

uthscTR_J3
```



### TR_J4

```{r}
uthscTR_J4 <- read.csv('UTHSC_report_tr_j4_2022-01-2024-12.csv', skip = 13) |>
  mutate(Location = 'Health Sciences',
         Total_Usage = Reporting_Period_Total) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan.2022`) == FALSE, `Jan.2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb.2022`) == FALSE, `Feb.2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar.2022`) == FALSE, `Mar.2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr.2022`) == FALSE, `Apr.2022`, 0),
         `May-2022` = ifelse(is.na(`May.2022`) == FALSE, `May.2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun.2022`) == FALSE, `Jun.2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul.2022`) == FALSE, `Jul.2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug.2022`) == FALSE, `Aug.2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep.2022`) == FALSE, `Sep.2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct.2022`) == FALSE, `Oct.2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov.2022`) == FALSE, `Nov.2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec.2022`) == FALSE, `Dec.2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan.2023`) == FALSE, `Jan.2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb.2023`) == FALSE, `Feb.2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar.2023`) == FALSE, `Mar.2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr.2023`) == FALSE, `Apr.2023`, 0),
         `May-2023` = ifelse(is.na(`May.2023`) == FALSE, `May.2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun.2023`) == FALSE, `Jun.2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul.2023`) == FALSE, `Jul.2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug.2023`) == FALSE, `Aug.2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep.2023`) == FALSE, `Sep.2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct.2023`) == FALSE, `Oct.2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov.2023`) == FALSE, `Nov.2023`, 0),
         `Dec-2023` = ifelse(is.na(`Dec.2023`) == FALSE, `Dec.2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan.2024`) == FALSE, `Jan.2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb.2024`) == FALSE, `Feb.2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar.2024`) == FALSE, `Mar.2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr.2024`) == FALSE, `Apr.2024`, 0),
         `May-2024` = ifelse(is.na(`May.2024`) == FALSE, `May.2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun.2024`) == FALSE, `Jun.2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul.2024`) == FALSE, `Jul.2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug.2024`) == FALSE, `Aug.2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep.2024`) == FALSE, `Sep.2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct.2024`) == FALSE, `Oct.2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov.2024`) == FALSE, `Nov.2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec.2024`) == FALSE, `Dec.2024`, 0)) |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, YOP, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`)

uthscTR_J4
```



# Clean Up the UTK Files to Match Other Column Structures



## TR_J1


```{r}
utkTR_J1 <- read_tsv('UTK-OUP-TRJ1-Jan2022-Dec2024.tsv', skip = 13) |>
  mutate(Total_Usage = Reporting_Period_Total,
         Location = 'UT Knoxville') |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan-2022`) == FALSE, `Jan-2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb-2022`) == FALSE, `Feb-2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar-2022`) == FALSE, `Mar-2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr-2022`) == FALSE, `Apr-2022`, 0),
         `May-2022` = ifelse(is.na(`May-2022`) == FALSE, `May-2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun-2022`) == FALSE, `Jun-2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul-2022`) == FALSE, `Jul-2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug-2022`) == FALSE, `Aug-2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep-2022`) == FALSE, `Sep-2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct-2022`) == FALSE, `Oct-2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov-2022`) == FALSE, `Nov-2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec-2022`) == FALSE, `Dec-2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan-2023`) == FALSE, `Jan-2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb-2023`) == FALSE, `Feb-2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar-2023`) == FALSE, `Mar-2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr-2023`) == FALSE, `Apr-2023`, 0),
         `May-2023` = ifelse(is.na(`May-2023`) == FALSE, `May-2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun-2023`) == FALSE, `Jun-2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul-2023`) == FALSE, `Jul-2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug-2023`) == FALSE, `Aug-2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep-2023`) == FALSE, `Sep-2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct-2023`) == FALSE, `Oct-2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov-2023`) == FALSE, `Nov-2023`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2023`) == FALSE, `Dec-2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan-2024`) == FALSE, `Jan-2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb-2024`) == FALSE, `Feb-2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar-2024`) == FALSE, `Mar-2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr-2024`) == FALSE, `Apr-2024`, 0),
         `May-2024` = ifelse(is.na(`May-2024`) == FALSE, `May-2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun-2024`) == FALSE, `Jun-2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul-2024`) == FALSE, `Jul-2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug-2024`) == FALSE, `Aug-2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep-2024`) == FALSE, `Sep-2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct-2024`) == FALSE, `Oct-2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov-2024`) == FALSE, `Nov-2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2024`) == FALSE, `Dec-2024`, 0))

utkTR_J1
```

## TR_J2



```{r}
utkTR_J2 <- read_tsv('UTK-OUP-TRJ2-Jan2022-Dec2024.tsv', skip = 13) |>
  mutate(Total_Usage = Reporting_Period_Total,
         Location = 'UT Knoxville') |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan-2022`) == FALSE, `Jan-2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb-2022`) == FALSE, `Feb-2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar-2022`) == FALSE, `Mar-2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr-2022`) == FALSE, `Apr-2022`, 0),
         `May-2022` = ifelse(is.na(`May-2022`) == FALSE, `May-2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun-2022`) == FALSE, `Jun-2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul-2022`) == FALSE, `Jul-2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug-2022`) == FALSE, `Aug-2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep-2022`) == FALSE, `Sep-2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct-2022`) == FALSE, `Oct-2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov-2022`) == FALSE, `Nov-2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec-2022`) == FALSE, `Dec-2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan-2023`) == FALSE, `Jan-2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb-2023`) == FALSE, `Feb-2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar-2023`) == FALSE, `Mar-2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr-2023`) == FALSE, `Apr-2023`, 0),
         `May-2023` = ifelse(is.na(`May-2023`) == FALSE, `May-2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun-2023`) == FALSE, `Jun-2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul-2023`) == FALSE, `Jul-2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug-2023`) == FALSE, `Aug-2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep-2023`) == FALSE, `Sep-2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct-2023`) == FALSE, `Oct-2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov-2023`) == FALSE, `Nov-2023`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2023`) == FALSE, `Dec-2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan-2024`) == FALSE, `Jan-2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb-2024`) == FALSE, `Feb-2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar-2024`) == FALSE, `Mar-2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr-2024`) == FALSE, `Apr-2024`, 0),
         `May-2024` = ifelse(is.na(`May-2024`) == FALSE, `May-2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun-2024`) == FALSE, `Jun-2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul-2024`) == FALSE, `Jul-2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug-2024`) == FALSE, `Aug-2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep-2024`) == FALSE, `Sep-2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct-2024`) == FALSE, `Oct-2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov-2024`) == FALSE, `Nov-2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2024`) == FALSE, `Dec-2024`, 0))

utkTR_J2
```



## TR_J3



```{r}
utkTR_J3 <- read_tsv('UTK-OUP-TRJ3-Jan2022-Dec2024.tsv', skip = 13) |>
  mutate(Total_Usage = Reporting_Period_Total,
         Location = 'UT Knoxville') |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Access_Type, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan-2022`) == FALSE, `Jan-2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb-2022`) == FALSE, `Feb-2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar-2022`) == FALSE, `Mar-2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr-2022`) == FALSE, `Apr-2022`, 0),
         `May-2022` = ifelse(is.na(`May-2022`) == FALSE, `May-2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun-2022`) == FALSE, `Jun-2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul-2022`) == FALSE, `Jul-2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug-2022`) == FALSE, `Aug-2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep-2022`) == FALSE, `Sep-2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct-2022`) == FALSE, `Oct-2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov-2022`) == FALSE, `Nov-2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec-2022`) == FALSE, `Dec-2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan-2023`) == FALSE, `Jan-2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb-2023`) == FALSE, `Feb-2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar-2023`) == FALSE, `Mar-2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr-2023`) == FALSE, `Apr-2023`, 0),
         `May-2023` = ifelse(is.na(`May-2023`) == FALSE, `May-2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun-2023`) == FALSE, `Jun-2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul-2023`) == FALSE, `Jul-2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug-2023`) == FALSE, `Aug-2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep-2023`) == FALSE, `Sep-2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct-2023`) == FALSE, `Oct-2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov-2023`) == FALSE, `Nov-2023`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2023`) == FALSE, `Dec-2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan-2024`) == FALSE, `Jan-2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb-2024`) == FALSE, `Feb-2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar-2024`) == FALSE, `Mar-2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr-2024`) == FALSE, `Apr-2024`, 0),
         `May-2024` = ifelse(is.na(`May-2024`) == FALSE, `May-2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun-2024`) == FALSE, `Jun-2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul-2024`) == FALSE, `Jul-2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug-2024`) == FALSE, `Aug-2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep-2024`) == FALSE, `Sep-2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct-2024`) == FALSE, `Oct-2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov-2024`) == FALSE, `Nov-2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2024`) == FALSE, `Dec-2024`, 0))

utkTR_J3
```



## TR_J4


```{r}
utkTR_J4 <- read_tsv('UTK-OUP-TRJ4-Jan2022-Dec2024.tsv', skip = 13) |>
  mutate(Total_Usage = Reporting_Period_Total,
         Location = 'UT Knoxville') |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, YOP, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan-2022`) == FALSE, `Jan-2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb-2022`) == FALSE, `Feb-2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar-2022`) == FALSE, `Mar-2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr-2022`) == FALSE, `Apr-2022`, 0),
         `May-2022` = ifelse(is.na(`May-2022`) == FALSE, `May-2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun-2022`) == FALSE, `Jun-2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul-2022`) == FALSE, `Jul-2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug-2022`) == FALSE, `Aug-2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep-2022`) == FALSE, `Sep-2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct-2022`) == FALSE, `Oct-2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov-2022`) == FALSE, `Nov-2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec-2022`) == FALSE, `Dec-2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan-2023`) == FALSE, `Jan-2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb-2023`) == FALSE, `Feb-2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar-2023`) == FALSE, `Mar-2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr-2023`) == FALSE, `Apr-2023`, 0),
         `May-2023` = ifelse(is.na(`May-2023`) == FALSE, `May-2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun-2023`) == FALSE, `Jun-2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul-2023`) == FALSE, `Jul-2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug-2023`) == FALSE, `Aug-2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep-2023`) == FALSE, `Sep-2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct-2023`) == FALSE, `Oct-2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov-2023`) == FALSE, `Nov-2023`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2023`) == FALSE, `Dec-2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan-2024`) == FALSE, `Jan-2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb-2024`) == FALSE, `Feb-2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar-2024`) == FALSE, `Mar-2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr-2024`) == FALSE, `Apr-2024`, 0),
         `May-2024` = ifelse(is.na(`May-2024`) == FALSE, `May-2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun-2024`) == FALSE, `Jun-2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul-2024`) == FALSE, `Jul-2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug-2024`) == FALSE, `Aug-2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep-2024`) == FALSE, `Sep-2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct-2024`) == FALSE, `Oct-2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov-2024`) == FALSE, `Nov-2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2024`) == FALSE, `Dec-2024`, 0))

utkTR_J4
```



# Row Bind Like File Types


```{r}
TR_J1 <- plyr::rbind.fill(utcTR_J1, uthscTR_J1, utkTR_J1) |>
  filter(Metric_Type == 'Unique_Item_Requests')
TR_J2 <- plyr::rbind.fill(utcTR_J2, uthscTR_J2, utkTR_J2) |>
  filter(Metric_Type == 'No_License')
TR_J3 <- plyr::rbind.fill(utcTR_J3, uthscTR_J3, utkTR_J3) |>
  filter(Metric_Type == 'Unique_Item_Requests')
TR_J4 <- plyr::rbind.fill(utcTR_J4, uthscTR_J4, utkTR_J4) |>
  filter(Metric_Type == 'Unique_Item_Requests')
```





# UT Knoxville Book Reports

## TR_B1


```{r}
utkTR_B1 <- read_tsv('UTK-OUP-TRB1-Jan2022-Dec2024.tsv', skip = 13) |>
  mutate(Total_Usage = Reporting_Period_Total,
         Location = 'UT Knoxville') |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan-2022`) == FALSE, `Jan-2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb-2022`) == FALSE, `Feb-2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar-2022`) == FALSE, `Mar-2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr-2022`) == FALSE, `Apr-2022`, 0),
         `May-2022` = ifelse(is.na(`May-2022`) == FALSE, `May-2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun-2022`) == FALSE, `Jun-2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul-2022`) == FALSE, `Jul-2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug-2022`) == FALSE, `Aug-2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep-2022`) == FALSE, `Sep-2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct-2022`) == FALSE, `Oct-2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov-2022`) == FALSE, `Nov-2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec-2022`) == FALSE, `Dec-2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan-2023`) == FALSE, `Jan-2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb-2023`) == FALSE, `Feb-2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar-2023`) == FALSE, `Mar-2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr-2023`) == FALSE, `Apr-2023`, 0),
         `May-2023` = ifelse(is.na(`May-2023`) == FALSE, `May-2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun-2023`) == FALSE, `Jun-2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul-2023`) == FALSE, `Jul-2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug-2023`) == FALSE, `Aug-2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep-2023`) == FALSE, `Sep-2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct-2023`) == FALSE, `Oct-2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov-2023`) == FALSE, `Nov-2023`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2023`) == FALSE, `Dec-2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan-2024`) == FALSE, `Jan-2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb-2024`) == FALSE, `Feb-2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar-2024`) == FALSE, `Mar-2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr-2024`) == FALSE, `Apr-2024`, 0),
         `May-2024` = ifelse(is.na(`May-2024`) == FALSE, `May-2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun-2024`) == FALSE, `Jun-2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul-2024`) == FALSE, `Jul-2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug-2024`) == FALSE, `Aug-2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep-2024`) == FALSE, `Sep-2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct-2024`) == FALSE, `Oct-2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov-2024`) == FALSE, `Nov-2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2024`) == FALSE, `Dec-2024`, 0))

utkTR_B1
```

## TR_B2



```{r}
utkTR_B2 <- read_tsv('UTK-OUP-TRB2-Jan2022-Dec2024.tsv', skip = 13) |>
  mutate(Total_Usage = Reporting_Period_Total,
         Location = 'UT Knoxville') |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan-2022`) == FALSE, `Jan-2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb-2022`) == FALSE, `Feb-2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar-2022`) == FALSE, `Mar-2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr-2022`) == FALSE, `Apr-2022`, 0),
         `May-2022` = ifelse(is.na(`May-2022`) == FALSE, `May-2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun-2022`) == FALSE, `Jun-2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul-2022`) == FALSE, `Jul-2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug-2022`) == FALSE, `Aug-2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep-2022`) == FALSE, `Sep-2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct-2022`) == FALSE, `Oct-2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov-2022`) == FALSE, `Nov-2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec-2022`) == FALSE, `Dec-2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan-2023`) == FALSE, `Jan-2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb-2023`) == FALSE, `Feb-2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar-2023`) == FALSE, `Mar-2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr-2023`) == FALSE, `Apr-2023`, 0),
         `May-2023` = ifelse(is.na(`May-2023`) == FALSE, `May-2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun-2023`) == FALSE, `Jun-2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul-2023`) == FALSE, `Jul-2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug-2023`) == FALSE, `Aug-2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep-2023`) == FALSE, `Sep-2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct-2023`) == FALSE, `Oct-2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov-2023`) == FALSE, `Nov-2023`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2023`) == FALSE, `Dec-2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan-2024`) == FALSE, `Jan-2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb-2024`) == FALSE, `Feb-2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar-2024`) == FALSE, `Mar-2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr-2024`) == FALSE, `Apr-2024`, 0),
         `May-2024` = ifelse(is.na(`May-2024`) == FALSE, `May-2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun-2024`) == FALSE, `Jun-2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul-2024`) == FALSE, `Jul-2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug-2024`) == FALSE, `Aug-2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep-2024`) == FALSE, `Sep-2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct-2024`) == FALSE, `Oct-2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov-2024`) == FALSE, `Nov-2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2024`) == FALSE, `Dec-2024`, 0))

utkTR_B2
```



## TR_B3



```{r}
utkTR_B3 <- read_tsv('UTK-OUP-TRB3-Jan2022-Dec2024.tsv', skip = 13) |>
  mutate(Total_Usage = Reporting_Period_Total,
         Location = 'UT Knoxville') |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, Print_ISSN, Online_ISSN, URI, Access_Type, Metric_Type, Location, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan-2022`) == FALSE, `Jan-2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb-2022`) == FALSE, `Feb-2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar-2022`) == FALSE, `Mar-2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr-2022`) == FALSE, `Apr-2022`, 0),
         `May-2022` = ifelse(is.na(`May-2022`) == FALSE, `May-2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun-2022`) == FALSE, `Jun-2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul-2022`) == FALSE, `Jul-2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug-2022`) == FALSE, `Aug-2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep-2022`) == FALSE, `Sep-2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct-2022`) == FALSE, `Oct-2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov-2022`) == FALSE, `Nov-2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec-2022`) == FALSE, `Dec-2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan-2023`) == FALSE, `Jan-2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb-2023`) == FALSE, `Feb-2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar-2023`) == FALSE, `Mar-2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr-2023`) == FALSE, `Apr-2023`, 0),
         `May-2023` = ifelse(is.na(`May-2023`) == FALSE, `May-2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun-2023`) == FALSE, `Jun-2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul-2023`) == FALSE, `Jul-2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug-2023`) == FALSE, `Aug-2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep-2023`) == FALSE, `Sep-2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct-2023`) == FALSE, `Oct-2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov-2023`) == FALSE, `Nov-2023`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2023`) == FALSE, `Dec-2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan-2024`) == FALSE, `Jan-2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb-2024`) == FALSE, `Feb-2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar-2024`) == FALSE, `Mar-2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr-2024`) == FALSE, `Apr-2024`, 0),
         `May-2024` = ifelse(is.na(`May-2024`) == FALSE, `May-2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun-2024`) == FALSE, `Jun-2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul-2024`) == FALSE, `Jul-2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug-2024`) == FALSE, `Aug-2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep-2024`) == FALSE, `Sep-2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct-2024`) == FALSE, `Oct-2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov-2024`) == FALSE, `Nov-2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2024`) == FALSE, `Dec-2024`, 0))

utkTR_B3
```




# Import the Journal List and Journal Information from OUP's Website


## All Title List


```{r}
allList <- read.delim('OUP_2025_JournalsAllTitles.txt')

allList
```


## Clean Up ISSN Information to Join to Usage

This involves both filling some missing gaps and editing some slight differences in ISSNs (typically revolving around the X in it).


```{r}
cleanList <- allList |>
  mutate(online_identifier = case_when(
    publication_title == 'Interdisciplinary Cardiovascular and Thoracic Surgery' ~ '2753-670X',
    publication_title == 'Letters in Applied Microbiology' ~ '1472-765X',
    publication_title == 'Music Therapy' ~ '0734-7367',
    publication_title == 'Proceedings of the London Mathematical Society' ~ '1460-244X',
    publication_title == 'Progress of Theoretical Physics Supplement' ~ '0375-9867',
    publication_title == 'Review of Finance' ~ '1875-824X',
    .default = online_identifier
  ))

cleanTR_J1 <- TR_J1 |>
  mutate(Online_ISSN = case_when(
    Title == 'Music Therapy' ~ '0734-7367',
    Title == 'Progress of Theoretical Physics Supplement' ~ '0375-9687',
    .default = Online_ISSN
  ))

cleanTR_J3 <- TR_J3 |>
  mutate(Online_ISSN = case_when(
    Title == 'Music Therapy' ~ '0734-7367',
    Title == 'Progress of Theoretical Physics Supplement' ~ '0375-9687',
    .default = Online_ISSN
  ))

cleanTR_J4 <- TR_J4 |>
  mutate(Online_ISSN = case_when(
    Title == 'Music Therapy' ~ '0734-7367',
    Title == 'Progress of Theoretical Physics Supplement' ~ '0375-9687',
    .default = Online_ISSN
  ))
```


**THIS LIST INCLUDES OPEN ACCESS**


```{r}
midTR_J1 <- left_join(cleanTR_J1, cleanList, by = c('Online_ISSN' = 'online_identifier')) |>
  filter(Metric_Type == 'Unique_Item_Requests')

midTR_J1
```


```{r}
midTR_J3 <- left_join(cleanTR_J3, cleanList, by = c('Online_ISSN' = 'online_identifier')) |>
  filter(Metric_Type == 'Unique_Item_Requests')

midTR_J3
```



```{r}
midTR_J4 <- left_join(cleanTR_J4, cleanList, by = c('Online_ISSN' = 'online_identifier')) |>
  filter(Metric_Type == 'Unique_Item_Requests')

midTR_J4
```



## Title Price List


```{r}
costList <- read_excel('MASTER_2025_Institutional_pricelist_.xlsx') |>
  distinct()

costList
```


## Gather Only the Online, Institutional Prices


```{r}
filteredCost <- costList |>
  filter(Format != 'Print') |>
  filter(`Customer type` != 'Corporate')

filteredCost
```



## Clean up Single Title Filterings

```{r}
filteredCost2 <- filteredCost |>
  filter(Region != 'UK' | is.na(Region) == TRUE) |>
  filter(Region != 'Japan' | is.na(Region) == TRUE) |>
  filter(Category != 'High Schools' | is.na(Category) == TRUE) |>
  filter(!Category %in% c('L1: Public Libraries User Population under 50,000', 
                          'L2: Public Libraries User Population from 50,000 to 99,999', 
                          'L3: Public Libraries  User Population from 100,000 to 249,999',
                          'L4: Public Libraries  User Population from 250,000 to 500,000',
                          'L5: Public Libraries User Population 500,000 and above',
                          '1: Museums, Public Libs, Sec Schools',
                          '2: Community Colleges, not-for-profits',
                          'Schools rate',
                          'HBCU - Historically Black Colleges and Universities',
                          'Tribal Colleges') | is.na(Category) == TRUE) |>
  filter(Journal != 'Journal of American History' | is.na(Tier) == FALSE) |>
  filter(!Journal %in% c('Plant Physiology and The Plant Cell combined Online access FTE 1,000 TO 2,999',
                         'Plant Physiology and The Plant Cell combined Online access FTE 3,000 to 9,999',
                         'Plant Physiology and The Plant Cell combined Online access FTE under 1K')) |>
  mutate(Journal = case_when(
    Journal == 'Clinical Chemistry and Journal of Applied Laboratory Medicine' ~ 'Clinical Chemistry',
    .default = Journal
  )) |>
  mutate(`Online ISSN` = case_when(
    Journal == 'Clinical Chemistry' ~ '1530-8561',
    Journal == 'Journal of Applied Microbiology' ~ '1365-2672',
    Journal == 'Letters in Applied Microbiology' ~ '1472-765X',
    Journal == 'Journal of Communication' ~ '1460-2466',
    Journal == 'Human Communication Research' ~ '1468-2958',
    Journal == 'Communication Theory' ~ '1468-2885',
    Journal == 'Communication Culture & Critique' ~ '1753-9137',
    Journal == 'Journal of Public Administration Research and Theory' ~ '1477-9803',
    Journal == 'Perspectives on Public Management and Governance' ~ '2398-4929',
    Journal == 'Journal of the Royal Statistical Society Series A: Statistics in Society & Significance' ~ '1467-985X',
    Journal == 'Plant Physiology' ~ '1532-2548',
    Journal == 'The Plant Cell' ~ '1532-298X',
    Journal == 'Public Opinion Quarterly' ~ '1537-5331',
    Journal == 'Journal of Survey Statistics and Methodology' ~ '2325-0992',
    Journal == 'Sexual Medicine Reviews' ~ '2050-0521',
    Journal == 'The Journal of Sexual Medicine' ~ '1743-6109',
    Journal == 'The Review of Financial Studies' ~ '1465-7368',
    Journal == 'The Review of Asset Pricing Studies' ~ '2045-9939',
    Journal == 'The Review of Corporate Finance Studies' ~ '2046-9136',
    Journal == 'Transactions of the American Fisheries Society' ~ '1548-8659',
    .default = `Online ISSN`
  ))
```


## Get the Required Costs for Each Title and Location


```{r, warning = FALSE}
titles <- unique(filteredCost2$Journal)

titleVector <- c()
issnVector <- c()
costVector <- c()
locationVector <- c()


for(i in 1:length(titles)){
  titleData <- filteredCost2 |>
    filter(Journal == titles[i])
  
  # Check for multiple options for Format
  if(length(unique(titleData$Format)) > 1){
    titleData <- titleData |>
      filter(Format == 'Online-only access')
  }
  # Check for Multiple Tiers
  numberOfTiers <- length(unique(titleData$Tier))
  for(j in 1:numberOfTiers){
    min <- gsub(',', '', str_split(titleData$Tier[j], ' ', simplify = FALSE)[[1]][2])
    max <- gsub(',', '', str_split(titleData$Tier[j], ' ', simplify = FALSE)[[1]][4])
    min <- ifelse(is.na(as.numeric(min)) == TRUE, -5000, as.numeric(min))
    max <- ifelse(is.na(as.numeric(max)) == TRUE, 1000000, as.numeric(max))
    if(min < 39995 & max > 39995){
      titleVector <- append(titleVector, titles[i])
      issnVector <- append(issnVector, titleData$`Online ISSN`[1])
      costVector <- append(costVector, titleData$`USD price`[j])
      locationVector <- append(locationVector, 'UT Knoxville')
    }
    if(min < 11995 & max > 11995){
      titleVector <- append(titleVector, titles[i])
      issnVector <- append(issnVector, titleData$`Online ISSN`[1])
      costVector <- append(costVector, titleData$`USD price`[j])
      locationVector <- append(locationVector, 'UT Chattanooga')
    }
    if(min < 3495 & max > 3495){
      titleVector <- append(titleVector, titles[i])
      issnVector <- append(issnVector, titleData$`Online ISSN`[1])
      costVector <- append(costVector, titleData$`USD price`[j])
      locationVector <- append(locationVector, 'Health Sciences')
    }
  }
}

costDataFrame <- data.frame(
  Title = titleVector,
  Online_ISSN = issnVector,
  Location = locationVector,
  Price = costVector
)

costDataFrame
```


```{r, warning = FALSE}
fullTR_J1 <- left_join(midTR_J1, costDataFrame, by = c('Online_ISSN', 'Location')) |>
  mutate(Price = ifelse(grepl('Open Access', Collections) == TRUE, 0, Price))


fullTR_J3 <- left_join(midTR_J3, costDataFrame, by = c('Online_ISSN', 'Location')) |>
  mutate(Price = ifelse(grepl('Open Access', Collections) == TRUE, 0, Price))

fullTR_J4 <- left_join(midTR_J4, costDataFrame, by = c('Online_ISSN', 'Location')) |>
  mutate(Price = ifelse(grepl('Open Access', Collections) == TRUE, 0, Price))
```





## Load in Total Price of OUP Packages


This comes from the previous order cost.



```{r}
oupPrice <- data.frame(
  Location = c('UT Knoxville', 'Health Sciences', 'UT Chattanooga'),
  Price = c(187703.47, 59693.35, 50596.18)
)
```



## Get Mean Prices per Campus

This will fill in any gaps in price below.

```{r}
utk <- fullTR_J1 |>
  filter(Location == 'UT Knoxville')

utkMedPrice <- mean(utk$Price, na.rm = TRUE)

utkMedPrice


utc <- fullTR_J1 |>
  filter(Location == 'UT Chattanooga')

utcMedPrice <- mean(utc$Price, na.rm = TRUE)

utcMedPrice


uthsc <- fullTR_J1 |>
  filter(Location == 'Health Sciences')

uthscMedPrice <- mean(uthsc$Price, na.rm = TRUE)

uthscMedPrice
```



# Look at Usage Trends



## Grand Total Usage



```{r}
TR_J4_Complete <- fullTR_J4 |>
  group_by(Title.x, Location, YOP, Metric_Type, Subject, Collections, Price) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE)) |>
  ungroup() |>  
  mutate(Subject = ifelse(is.na(Subject) == TRUE, 'Unknown', Subject),
         Collections = ifelse(is.na(Collections) == TRUE, 'Unknown', Collections)) |>
  mutate(Price = case_when(
    Location == 'UT Knoxville' & is.na(Price) == TRUE ~ utkMedPrice,
    Location == 'UT Chattanooga' & is.na(Price) == TRUE ~ utcMedPrice,
    Location == 'Health Sciences' & is.na(Price) == TRUE ~ uthscMedPrice,
    .default = Price
  )) |>
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24) |>
  mutate(isCC22 = ifelse((YOP >= 2018 & YOP <= 2022) | YOP == 9999, 'Yes', 'No'),
         isCC23 = ifelse((YOP >= 2019 & YOP <= 2023) | YOP == 9999, 'Yes', 'No'),
         isCC24 = ifelse(YOP >= 2020, 'Yes', 'No')) |>
  mutate(isBackfile22 = ifelse(YOP > 1997 & YOP < 2018, 'Yes', 'No'),
         isBackfile23 = ifelse(YOP > 1997 & YOP < 2019, 'Yes', 'No'),
         isBackfile24 = ifelse(YOP > 1997 & YOP < 2020, 'Yes', 'No')) |>
  mutate(isTrueBackfile = ifelse(YOP <= 1997, 'Yes', 'No')) |>
  mutate(currentYearUsage = case_when(
    YOP == 2022 ~ usage22,
    YOP == 2023 ~ usage23,
    YOP == 2024 ~ usage24,
    .default = 0),
         ccClearanceUsage = case_when(
           isCC22 == 'Yes' & isCC23 == 'No' & isCC24 == 'No' ~ usage22,
           isCC22 == 'Yes' & isCC23 == 'Yes' & isCC24 == 'No' ~ usage22 + usage23,
           isCC22 == 'Yes' & isCC23 == 'Yes' & isCC24 == 'Yes' ~ usage22 + usage23 + usage24,
           isCC22 == 'No' & isCC23 == 'Yes' & isCC24 == 'Yes' ~ usage23 + usage24,
           isCC22 == 'No' & isCC23 == 'No' & isCC24 == 'Yes' ~ usage24,
           isCC22 == 'No' & isCC23 == 'No' & isCC24 == 'No' ~ 0,
           .default = NA
         ),
        backfileUsage = case_when(
           isBackfile22 == 'Yes' & isBackfile23 == 'No' & isBackfile24 == 'No' ~ usage22,
           isBackfile22 == 'Yes' & isBackfile23 == 'Yes' & isBackfile24 == 'No' ~ usage22 + usage23,
           isBackfile22 == 'Yes' & isBackfile23 == 'Yes' & isBackfile24 == 'Yes' ~ usage22 + usage23 + usage24,
           isBackfile22 == 'No' & isBackfile23 == 'Yes' & isBackfile24 == 'Yes' ~ usage23 + usage24,
           isBackfile22 == 'No' & isBackfile23 == 'No' & isBackfile24 == 'Yes' ~ usage24,
           isBackfile22 == 'No' & isBackfile23 == 'No' & isBackfile24 == 'No' ~ 0,
           .default = NA          
        ),
        trueBackFileUsage = ifelse(isTrueBackfile == 'Yes', Total_Usage, 0)
  )

TR_J4_Complete |>
  arrange(desc(ccClearanceUsage))
```






# TR_J1: Usage by Package Type and Individual Title Cost/Use



```{r}
TR_J1_Complete <- fullTR_J1 |>
  group_by(Title.x, Location, Metric_Type, Subject, Collections, Price) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE)) |>
  ungroup() |>
  mutate(Subject = ifelse(is.na(Subject) == TRUE | Subject == '', 'Unknown', Subject),
         Collections = ifelse(is.na(Collections) == TRUE | Collections == '', 'Unknown', Collections)) |>
  mutate(Price = case_when(
    Location == 'UT Knoxville' & is.na(Price) == TRUE ~ utkMedPrice,
    Location == 'UT Chattanooga' & is.na(Price) == TRUE ~ utcMedPrice,
    Location == 'Health Sciences' & is.na(Price) == TRUE ~ uthscMedPrice,
    .default = Price
  )) |>
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24) |>
  mutate(fullCollectionUsage = ifelse(grepl('Unknown', Collections, fixed = FALSE) == FALSE & grepl('Open Access', Collections, fixed = FALSE) == FALSE, Total_Usage, 0),
         clinMedCollectionUsage = ifelse(grepl('Clinical Medicine', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         econCollectionUsage = ifelse(grepl('Economics & Finance', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         hssCollectionUsage = ifelse(grepl('HSS', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         humanitiesCollectionUsage = ifelse(grepl('Humanities', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         lawCollectionUsage = ifelse(grepl('Law', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         lifeScienceCollectionUsage = ifelse(grepl('Life Sciences', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         mathCollectionUsage = ifelse(grepl('Mathematics & Physical Sciences', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         medCollectionUsage = ifelse(grepl('Medicine,', Collections, fixed = FALSE) == TRUE | Collections == 'Medicine', Total_Usage, 0),
         policyCollectionUsage = ifelse(grepl('Policy', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         religionCollectionUsage = ifelse(grepl('Religion & Philosophy', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         socSciCollectionUsage = ifelse(grepl('Social Sciences', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         stmCollectionUsage = ifelse(grepl('STM', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         oaCollectionUsage = ifelse(grepl('Open Access', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         unknownCollectionUsage = ifelse(Collections == 'Unknown', Total_Usage, 0)) |>
  mutate(costUse = Price / (Total_Usage / 3))|>
  mutate(costUseBucket = case_when(
    Collections == 'Open Access' ~ 'Full Open Access',
    costUse < 20 ~ 'Under $20',
    costUse >= 20 ~ 'Over $20'
  )
)

TR_J1_Complete
```




# TR_J3: Usage by OA Type, Including OA Titles



```{r}
TR_J3_Complete <- fullTR_J3 |>
  group_by(Title.x, Location, Access_Type, Metric_Type, Subject, Collections) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE)) |>
  ungroup() |>
  mutate(Subject = ifelse(is.na(Subject) == TRUE | Subject == '', 'Unknown', Subject),
         Collections = ifelse(is.na(Collections) == TRUE | Collections == '', 'Unknown', Collections)) |>
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24) |>
  mutate(fullCollectionUsage = ifelse(grepl('Unknown', Collections, fixed = FALSE) == FALSE & grepl('Open Access', Collections, fixed = FALSE) == FALSE, Total_Usage, 0),
         clinMedCollectionUsage = ifelse(grepl('Clinical Medicine', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         econCollectionUsage = ifelse(grepl('Economics & Finance', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         hssCollectionUsage = ifelse(grepl('HSS', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         humanitiesCollectionUsage = ifelse(grepl('Humanities', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         lawCollectionUsage = ifelse(grepl('Law', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         lifeScienceCollectionUsage = ifelse(grepl('Life Sciences', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         mathCollectionUsage = ifelse(grepl('Mathematics & Physical Sciences', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         medCollectionUsage = ifelse(grepl('Medicine,', Collections, fixed = FALSE) == TRUE | Collections == 'Medicine', Total_Usage, 0),
         policyCollectionUsage = ifelse(grepl('Policy', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         religionCollectionUsage = ifelse(grepl('Religion & Philosophy', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         socSciCollectionUsage = ifelse(grepl('Social Sciences', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         stmCollectionUsage = ifelse(grepl('STM', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         oaCollectionUsage = ifelse(grepl('Open Access', Collections, fixed = FALSE) == TRUE, Total_Usage, 0),
         unknownCollectionUsage = ifelse(Collections == 'Unknown', Total_Usage, 0))

TR_J3_Complete
```



# Add the Cost/Use Bucket and the Price from TR_Complete to TR_J4_Complete



```{r, warning = FALSE}
smallTRComplete <- TR_J1_Complete |>
  select(Title.x, Location, Collections, costUseBucket, Price)

TR_J4_Export <- left_join(TR_J4_Complete, smallTRComplete, by = c('Title.x' = 'Title.x', 'Location' = 'Location', 'Collections' = 'Collections', 'Price' = 'Price')) 
```



# Create the Copyright Clearance Bucket Column


```{r}
TR_J4_Buckets <- TR_J4_Export |>
  group_by(Title.x, Location, Collections, Price) |>
  summarise(copyrightClearanceUsage = sum(ccClearanceUsage)) |>
  mutate(ccCostUse = Price / (copyrightClearanceUsage / 3)) |>
  mutate(ccCostUseBucket = case_when(
    Collections == 'Open Access' ~ 'Full Open Access',
    ccCostUse < 20 ~ 'Under $20',
    ccCostUse >= 20 ~ 'Over $20'
  )) |>
  mutate(ccCostUse = ifelse(is.infinite(ccCostUse) == TRUE, 0, ccCostUse)) |>
  mutate(Collections = str_trim(Collections, side = 'both'))
```


```{r}
TR_J4_Export_Final <- left_join(TR_J4_Export, TR_J4_Buckets, by = c('Title.x' = 'Title.x', 'Location' = 'Location', 'Collections' = 'Collections', 'Price' = 'Price')) 
```


# Export the Data

```{r}
write.csv(TR_J4_Export_Final, 'OUP Usage by Year of Publishing.csv', row.names = FALSE)
```


# TR_Complete: Cost/Use by Campus



## TR_Complete: Total Usage by Campus


```{r}
TR_Complete_Usage = TR_J1_Complete |>
  group_by(Location) |>
  summarise(Titles = n(),
            Usage = sum(Total_Usage))

TR_Complete_Usage
```


## Compare Total Usage to the Total Cost


```{r}
costPerUseTotal <- inner_join(oupPrice, TR_Complete_Usage, by = 'Location') |>
  mutate(costUse = Price / (Usage / 3),
         costTitle = Price / Titles)

costPerUseTotal
```




```{r}
write.csv(costPerUseTotal, 'OUP Package Cost Per Use Summary.csv', row.names = FALSE)
```


# TR_Complete: Usage by Package


```{r}
TR_Package_Usage <- fullTR_J1 |>
  group_by(Title.x, Location, Metric_Type, Subject, Collections) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE)) |>
  ungroup() |>
  mutate(Subject = ifelse(is.na(Subject) == TRUE | Subject == '', 'Unknown', Subject),
         Collections = ifelse(is.na(Collections) == TRUE | Collections == '', 'Unknown', Collections)) |>
  mutate(splitCollection = strsplit(Collections, ', ')) |>
  unnest(splitCollection) |>
  mutate(splitCollection = case_when(
    splitCollection == 'Social Science' ~ 'Social Sciences',
    splitCollection == 'HSS ' ~ 'HSS',
    splitCollection == 'Maths & Physical Sciences' ~ 'Mathematics & Physical Sciences',
    splitCollection == 'Collection' ~ 'Medicine',
    splitCollection == 'Philosophy and Religion' ~ 'Religion & Philosophy',
    splitCollection == 'HSS Policy' ~ 'HSS, Policy',
    splitCollection == 'Life Science' ~ 'Life Sciences',
    .default = splitCollection
  )) |>
  mutate(splitCollection = strsplit(splitCollection, ', ')) |>
  unnest(splitCollection) |>
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24) |>
  group_by(Location, splitCollection) |>
  summarise(packageTitles = length(unique(Title.x)),
            packageUsage = sum(Total_Usage)) |>
  mutate(packageTitlePerc = case_when(
              Location == 'Health Sciences' ~ packageTitles / 289,
              Location == 'UT Chattanooga' ~ packageTitles / 417,
              Location == 'UT Knoxville' ~ packageTitles / 501
            ),
            packageUsagePerc = case_when(
              Location == 'Health Sciences' ~ packageUsage / 43344,
              Location == 'UT Chattanooga' ~ packageUsage / 19711,
              Location == 'UT Knoxville' ~ packageUsage / 120289
            )) |>
  mutate(usageOverExpected = packageUsagePerc - packageTitlePerc) |>
  distinct()

TR_Package_Usage
```





## Combine the Two Tables for Export


```{r}
TR_Package_And_CPU = inner_join(TR_Package_Usage, costPerUseTotal, by = 'Location') |>
  mutate(costTitle = Price / Titles)

write.csv(TR_Package_And_CPU, 'Campus Usage by Package and Overall Cost Per Use.csv', row.names = FALSE)
```



# Pivot Tables Longer for Line Graphs



```{r}
TR_Complete_Longer <- TR_J1_Complete |>
  pivot_longer(cols = contains('-'),
               names_to = 'Month',
               values_to = 'Usage') |>
  mutate(Collections = str_trim(Collections, side = 'both'))

write.csv(TR_Complete_Longer, 'OUP Title Use and Title Cost Per Use.csv', row.names = FALSE)
```



```{r}
TR_Complete_Longer_3 <- TR_J3_Complete |>
  pivot_longer(cols = contains('-'),
               names_to = 'Month',
               values_to = 'Usage') |>
  mutate(Collections = str_trim(Collections, side = 'both'))

write.csv(TR_Complete_Longer_3, 'OUP Usage by Access Type and Title.csv', row.names = FALSE)
```




```{r}
test <- TR_Complete_Longer_3 |>
  mutate(isGold = ifelse(Access_Type == 'OA_Gold', 1, 0),
         isControlled = ifelse(Access_Type == 'Controlled', 1, 0)) |>
  group_by(Title.x, Location) |>
  summarise(accessModes = length(unique(Access_Type)),
            Total_Usage = sum(Usage),
            isGold = sum(isGold),
            isControlled = sum(isControlled)) |>
  filter(isControlled == 0 & Location == 'UT Knoxville') |>
  arrange(accessModes)

test
```




# UT Knoxville TR_B3 - Filling in the Separate Usage Gaps

```{r}
cleanTR_B3 <- utkTR_B3 |>
  filter(Metric_Type == 'Unique_Item_Requests') |>
  group_by(Title, Online_ISSN, Metric_Type, Location) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE)) |>
  ungroup() |>  
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24)

cleanTR_B3
```


# Select the Separate Titles and Add Price and Cost/Use

## Single Titles

```{r}
selectTitles <- cleanTR_B3 |>
  filter(Title %in% c('Encyclopedia of Social Work', 'Anthropology', 'AMA Manual of Style', 'Oxford Bibliographies Online', 'Oxford Dictionary of National Biography', 'Oxford Reference Online', 'The World Shakespeare Bibliography', 'Grove Art Online', 'Grove Music Online', 'Oxford English Dictionary', 'Official Methods of Analysis of AOAC INTERNATIONAL'))

selectTitles
```


STILL NEED: Oxford Bibliographies Online, Oxford Reference Online, The World Shakespeare Bibliography, 

## Oxford Research Encyclopedias


```{r}
oxfordEncyclopedias <- cleanTR_B3 |>
  filter(grepl('Oxford Research Encyclopedia', Title, fixed = TRUE) == TRUE) |>
  mutate(Title = 'Oxford Research Encyclopedias') |>
  group_by(Title, Online_ISSN, Metric_Type, Location) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE)) |>
  ungroup() |>  
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24)

oxfordEncyclopedias
```



## Combine All Titles

```{r}
allSingleTitles <- selectTitles |> #rbind(selectTitles, oxfordEncyclopedias) |>
  arrange(Title)

allSingleTitles
```



## Add in Price and Find Cost/Use

```{r}
Price <- c(7500, 300, 300, 3019.28, 12503.64, 4624.80, 2311.48, 11720.59)

finalSingleTitles <- cbind(allSingleTitles, Price) |>
  mutate(usagePerYear = Total_Usage / 3) |>
  mutate(costUse = Price / usagePerYear) |>
  select(Title, Total_Usage, usagePerYear, Price, costUse)

finalSingleTitles
```



# Load in the PR for Platforms


```{r}
platformReport <- read_tsv('OUP-PRP1-Jan2022-Dec2024.tsv', skip = 13) |>
  mutate(Total_Usage = Reporting_Period_Total,
         Location = 'UT Knoxville') |>
  select(Platform, Metric_Type, Total_Usage,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`) |>
  mutate(`Jan-2022` = ifelse(is.na(`Jan-2022`) == FALSE, `Jan-2022`, 0),
         `Feb-2022` = ifelse(is.na(`Feb-2022`) == FALSE, `Feb-2022`, 0),
         `Mar-2022` = ifelse(is.na(`Mar-2022`) == FALSE, `Mar-2022`, 0),
         `Apr-2022` = ifelse(is.na(`Apr-2022`) == FALSE, `Apr-2022`, 0),
         `May-2022` = ifelse(is.na(`May-2022`) == FALSE, `May-2022`, 0),
         `Jun-2022` = ifelse(is.na(`Jun-2022`) == FALSE, `Jun-2022`, 0),
         `Jul-2022` = ifelse(is.na(`Jul-2022`) == FALSE, `Jul-2022`, 0),
         `Aug-2022` = ifelse(is.na(`Aug-2022`) == FALSE, `Aug-2022`, 0),
         `Sep-2022` = ifelse(is.na(`Sep-2022`) == FALSE, `Sep-2022`, 0),
         `Oct-2022` = ifelse(is.na(`Oct-2022`) == FALSE, `Oct-2022`, 0),
         `Nov-2022` = ifelse(is.na(`Nov-2022`) == FALSE, `Nov-2022`, 0),
         `Dec-2022` = ifelse(is.na(`Dec-2022`) == FALSE, `Dec-2022`, 0),
         `Jan-2023` = ifelse(is.na(`Jan-2023`) == FALSE, `Jan-2023`, 0),
         `Feb-2023` = ifelse(is.na(`Feb-2023`) == FALSE, `Feb-2023`, 0),
         `Mar-2023` = ifelse(is.na(`Mar-2023`) == FALSE, `Mar-2023`, 0),
         `Apr-2023` = ifelse(is.na(`Apr-2023`) == FALSE, `Apr-2023`, 0),
         `May-2023` = ifelse(is.na(`May-2023`) == FALSE, `May-2023`, 0),
         `Jun-2023` = ifelse(is.na(`Jun-2023`) == FALSE, `Jun-2023`, 0),
         `Jul-2023` = ifelse(is.na(`Jul-2023`) == FALSE, `Jul-2023`, 0),
         `Aug-2023` = ifelse(is.na(`Aug-2023`) == FALSE, `Aug-2023`, 0),
         `Sep-2023` = ifelse(is.na(`Sep-2023`) == FALSE, `Sep-2023`, 0),
         `Oct-2023` = ifelse(is.na(`Oct-2023`) == FALSE, `Oct-2023`, 0),
         `Nov-2023` = ifelse(is.na(`Nov-2023`) == FALSE, `Nov-2023`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2023`) == FALSE, `Dec-2023`, 0),
         `Jan-2024` = ifelse(is.na(`Jan-2024`) == FALSE, `Jan-2024`, 0),
         `Feb-2024` = ifelse(is.na(`Feb-2024`) == FALSE, `Feb-2024`, 0),
         `Mar-2024` = ifelse(is.na(`Mar-2024`) == FALSE, `Mar-2024`, 0),
         `Apr-2024` = ifelse(is.na(`Apr-2024`) == FALSE, `Apr-2024`, 0),
         `May-2024` = ifelse(is.na(`May-2024`) == FALSE, `May-2024`, 0),
         `Jun-2024` = ifelse(is.na(`Jun-2024`) == FALSE, `Jun-2024`, 0),
         `Jul-2024` = ifelse(is.na(`Jul-2024`) == FALSE, `Jul-2024`, 0),
         `Aug-2024` = ifelse(is.na(`Aug-2024`) == FALSE, `Aug-2024`, 0),
         `Sep-2024` = ifelse(is.na(`Sep-2024`) == FALSE, `Sep-2024`, 0),
         `Oct-2024` = ifelse(is.na(`Oct-2024`) == FALSE, `Oct-2024`, 0),
         `Nov-2024` = ifelse(is.na(`Nov-2024`) == FALSE, `Nov-2024`, 0),
         `Dec-2024` = ifelse(is.na(`Dec-2024`) == FALSE, `Dec-2024`, 0))

platformReport
```


List: Encyclopedia of Social Work, Anthropology, AMA Manual of Style, Oxford Bibliographies Online, Oxford Dictionary of National Biography, Oxford Reference Online, The World Shakespeare Bibliography, Grove Art, Grove Music, Oxford English Dictionary, Official Methods of Analysis of AOAC International


# Select the Separate Titles and Add Price and Cost/Use

## Single Titles

```{r}
selectTitles <- platformReport |>
  filter(Platform %in% c('Encyclopedia of Social Work', 'AMA Manual of Style', 'Oxford Bibliographies', 'Oxford Dictionary of National Biography', 'Oxford Reference', 'World Shakespeare Bibliography', 'Grove Art Online', 'Grove Music Online', 'Oxford English Dictionary', 'Official Methods of Analysis of AOAC INTERNATIONAL')) |>
  filter(Metric_Type == 'Unique_Item_Requests' | Platform == 'World Shakespeare Bibliography')

selectTitles
```


## Add in Price and Find Cost/Use

```{r}
Price <- c(7500, 3019.28, 12503.64, 3500, 2311.48, 11720.59, 2860.06, 432.60)

finalSingleTitles <- cbind(selectTitles, Price) |>
  mutate(usagePerYear = Total_Usage / 3) |>
  mutate(costUse = Price / usagePerYear) |>
  select(Platform, Total_Usage, usagePerYear, Price, costUse)

finalSingleTitles
```



