---
title: "Springer Usage Across UTK"
author: "Alexander Harriman"
date: "2024-12-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning = FALSE}
library(dplyr)
library(tidyverse)
library(gt)
library(stringr)
library(readxl)
library(ggplot2)
library(ggthemes)
library(janitor)
library(writexl)
```



# Load Data - UTK


## TR_J1


```{r}
TR_J1 <- read_excel('Springer-TRJ1-Jan2022-Jun2025.xlsx') |>
  mutate(Total_Usage = Reporting_Period_Total) |>
  group_by(Title, Print_ISSN, Online_ISSN, Total_Usage) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE),
    `Jan-2025` = sum(`Jan-2025`, na.rm = TRUE),
    `Feb-2025` = sum(`Feb-2025`, na.rm = TRUE),
    `Mar-2025` = sum(`Mar-2025`, na.rm = TRUE),
    `Apr-2025` = sum(`Apr-2025`, na.rm = TRUE),
    `May-2025` = sum(`May-2025`, na.rm = TRUE),
    `Jun-2025` = sum(`Jun-2025`, na.rm = TRUE))

TR_J1
```


## TR_J3



```{r}
TR_J3 <- read_excel('Springer-TRJ3-Jan2022-Jun2025.xlsx') |>
  mutate(Total_Usage = Reporting_Period_Total) |>
  group_by(Title, Print_ISSN, Online_ISSN, Access_Type, Total_Usage) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE),
    `Jan-2025` = sum(`Jan-2025`, na.rm = TRUE),
    `Feb-2025` = sum(`Feb-2025`, na.rm = TRUE),
    `Mar-2025` = sum(`Mar-2025`, na.rm = TRUE),
    `Apr-2025` = sum(`Apr-2025`, na.rm = TRUE),
    `May-2025` = sum(`May-2025`, na.rm = TRUE),
    `Jun-2025` = sum(`Jun-2025`, na.rm = TRUE))

TR_J3
```



## TR_J4


```{r}
TR_J4 <- read_excel('Springer-TRJ4-Jan2022-Jun2025.xlsx') |>
  mutate(Total_Usage = Reporting_Period_Total) |>
  group_by(Title, Print_ISSN, Online_ISSN, YOP, Total_Usage) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE),
    `Jan-2025` = sum(`Jan-2025`, na.rm = TRUE),
    `Feb-2025` = sum(`Feb-2025`, na.rm = TRUE),
    `Mar-2025` = sum(`Mar-2025`, na.rm = TRUE),
    `Apr-2025` = sum(`Apr-2025`, na.rm = TRUE),
    `May-2025` = sum(`May-2025`, na.rm = TRUE),
    `Jun-2025` = sum(`Jun-2025`, na.rm = TRUE))

TR_J4
```




# Import the Journal Price List from Springer's Website


```{r, warning = FALSE}
priceList <- read_excel('Springer Journal Price List.xlsx', skip = 4)

priceList
```



## Clean Up the Price List


```{r}
cleanPriceList <- priceList |>
  select(Title, `ISSN print`, `ISSN electronic`, `Institutional Price electronic only USD`) |>
  mutate(isOA = 'No')

colnames(cleanPriceList) <- c('Title', 'Print_ISSN', 'Online_ISSN', 'Price', 'isOA')

cleanPriceList
```



## Add in the OA Titles and Combine Lists

```{r}
oa <- read_excel('Springer OA Journal List.xlsx') |>
  select(Title, `ISSN print`, `ISSN electronic`) |>
  mutate(Price = 0,
         isOA = 'Yes')

colnames(oa) <- c('Title', 'Print_ISSN', 'Online_ISSN', 'Price', 'isOA')


allTitles <- rbind(cleanPriceList, oa)

allTitles
```





## Add in Institution Individual Title Prices


Some titles only have prices available via an institutional agreement. For those titles, the prices are available on SharePoint.


```{r}
indyPrices <- read_excel('Individual Prices in Institutional Agreement.xlsx')

indyPrices
```



```{r}
cleanAllTitles <- allTitles |>
  mutate(Price = case_when(
    Title == 'Acta Pharmacologica Sinica' ~ 1212.87,
    Title == 'Acta Politica' ~ 949.57,
    Title == 'Bone Marrow Transplantation' ~ 1714.47,
    Title == 'British Dental Journal' ~ 1318.91,
    Title == 'British Journal of Cancer' ~ 1719.23,
    Title == 'Cancer Gene Therapy' ~ 742.27,
    Title == 'Cell Death & Differentation' ~ 965.06,
    Title == 'Cell Research' ~ 1388.03,
    Title == 'Cellular & Molecular Immunology' ~ 476.58,
    Title == 'Comparative European Politics' ~ 1832.48,
    Title == 'Development' ~ 882.86,
    Title == 'Eastern Economic Journal' ~ 233.51,
    Title == 'European Journal of Clinical Nutrition' ~ 966.25,
    Title == 'European Journal of Human Genetics' ~ 1037.72,
    Title == 'Evidence-Based Dentistry' ~ 343.13,
    Title == 'Eye' ~ 785.15,
    Title == 'Gene Therapy' ~ 1471.42,
    Title == 'Genes & Immunity' ~ 442.02,
    Title == 'Heredity' ~ 571.88,
    Title == 'Hypertension Research' ~ 417,
    Title == 'Interest Groups & Advocacy' ~ 1135.68,
    Title == 'International Journal of Impotence Research' ~ 334.78,
    Title == 'International Journal of Obesity' ~ 1291.50,
    Title == 'Journal of Exposure Science & Environmental Epidemiology' ~ 617.16,
    Title == 'Journal of Human Genetics' ~ 505.16,
    Title == 'Journal of Human Hypertension' ~ 551.64,
    Title == 'Journal of International Business Studies' ~ 617.16,
    Title == 'Journal of Perinatology' ~ 294.28,
    Title == 'Lab Animal' ~ 1452.36,
    Title == 'Leukemia' ~ 2019.48,
    Title == 'Molecular Psychiatry' ~ 990.08,
    Title == 'Nature Biotechnology' ~ 3531.99,
    Title == 'Nature Catalysis' ~ 12946.95,
    Title == 'Nature Cell Biology' ~ 2875.94,
    Title == 'Nature Chemical Biology' ~ 4321.87,
    Title == 'Nature Chemistry' ~ 4445.13,
    Title == 'Nature Climate Change' ~ 3355.72,
    Title == 'Nature Ecology & Evolution' ~ 12946.95,
    Title == 'Nature Electronics' ~ 13331.47,
    Title == 'Nature Energy' ~ 3199.33,
    Title == 'Nature Genetics' ~ 3948.14,
    Title == 'Nature Geoscience' ~ 2931.62,
    Title == 'Nature Immunology' ~ 3962.35,
    Title == 'Nature Materials' ~ 3199.33,
    Title == 'Nature Medicine' ~ 3660.54,
    Title == 'Nature Methods' ~ 12448.74,
    Title == 'Nature Microbiology' ~ 3591.61,
    Title == 'Nature Nanotechnology' ~ 3199.33,
    Title == 'Nature Neuroscience' ~ 3418,
    Title == 'Nature Photonics' ~ 3590.30,
    Title == 'Nature Physics' ~ 3913.66,
    Title == 'Nature Plants' ~ 3657.88,
    Title == 'Nature Protocols' ~ 3139.69,
    Title == 'Nature Reviews Cancer' ~ 2995.25,
    Title == 'Nature Reviews Chemistry' ~ 11923.91,
    Title == 'Nature Reviews Clinical Oncology' ~ 13418.09,
    Title == 'Nature Reviews Drug Discovery' ~ 3138.36,
    Title == 'Nature Reviews Endocrinology' ~ 2995.23,
    Title == 'Nature Reviews Gastroenterology & Hepato' ~ 13418.09,
    Title == 'Nature Reviews Genetics' ~ 2996.54,
    Title == 'Nature Reviews Immunology' ~ 2875.94,
    Title == 'Nature Reviews Materials' ~ 2931.62,
    Title == 'Nature Reviews Microbiology' ~ 2848.12,
    Title == 'Nature Reviews Molecular Cell Biology' ~ 2875.94,
    Title == 'Nature Reviews Neuroscience' ~ 2996.54,
    Title == 'Nature Reviews Rheumatology' ~ 2996.54,
    Title == 'Nature Reviews Urology' ~ 2967.40,
    Title == 'Nature Structural & Molecular Biology' ~ 2875.93,
    Title == 'Nature' ~ 11487.88,
    Title == 'Neuropsychopharmacology' ~ 2250.62,
    Title == 'Oncogene' ~ 6128.74,
    Title == 'Pediatric Research' ~ 951.95,
    Title == 'Polymer Journal' ~ 1389.20,
    Title == 'Postdigital Science and Education' ~ 391.88,
    Title == 'postmedieval' ~ 1020.52,
    Title == 'Prostate Cancer and Prostatic Diseases' ~ 312.16,
    Title == 'Scientific American' ~ 2315.85,
    Title == 'The American Journal of Psychoanalysis' ~ 881.66,
    Title == 'The Journal of Antibiotics' ~ 483.73,
    Title == 'The Pharmacogenomics Journal' ~ 901.92,
    Title == 'Tropical Ecology' ~ 310.99,
    Title == 'Zeitschrift für Literaturwissenschaft und Linguistik' ~ 86.15,
    .default = Price
  ))
```






## Join Price to Usage



```{r, warning = FALSE}
fullTR_J1 <- left_join(TR_J1, cleanAllTitles, by = 'Online_ISSN') |>
  select(Title.x, Online_ISSN, Price, Total_Usage, isOA,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`,
         `Jan-2025`, `Feb-2025`, `Mar-2025`, `Apr-2025`, `May-2025`, `Jun-2025`)

fullTR_J3 <- left_join(TR_J3, cleanAllTitles, by = 'Online_ISSN') |>
  select(Title.x, Online_ISSN, Access_Type, Price, Total_Usage, isOA,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`,
         `Jan-2025`, `Feb-2025`, `Mar-2025`, `Apr-2025`, `May-2025`, `Jun-2025`)

fullTR_J4 <- left_join(TR_J4, cleanAllTitles, by = 'Online_ISSN') |>
  select(Title.x, Online_ISSN, YOP, Price, Total_Usage, isOA,
         `Jan-2022`, `Feb-2022`, `Mar-2022`, `Apr-2022`, `May-2022`, `Jun-2022`, `Jul-2022`, `Aug-2022`, `Sep-2022`, `Oct-2022`, `Nov-2022`, `Dec-2022`,
         `Jan-2023`, `Feb-2023`, `Mar-2023`, `Apr-2023`, `May-2023`, `Jun-2023`, `Jul-2023`, `Aug-2023`, `Sep-2023`, `Oct-2023`, `Nov-2023`, `Dec-2023`,
         `Jan-2024`, `Feb-2024`, `Mar-2024`, `Apr-2024`, `May-2024`, `Jun-2024`, `Jul-2024`, `Aug-2024`, `Sep-2024`, `Oct-2024`, `Nov-2024`, `Dec-2024`,
         `Jan-2025`, `Feb-2025`, `Mar-2025`, `Apr-2025`, `May-2025`, `Jun-2025`)
```








## Load in Total Price of Springer Package


This comes from the previous order cost.



```{r}
springerPrice <- data.frame(
  Location = c('UT Knoxville'),
  Price = c(794355.77)
)
```



## Get Mean Prices per Campus

This will fill in any gaps in price below.

```{r}
utkMedPrice <- mean(cleanPriceList$Price, na.rm = TRUE)

utkMedPrice
```



# Look at Usage Trends



## Grand Total Usage



```{r}
TR_J4_Complete <- fullTR_J4 |>
  group_by(Title.x, YOP, Price, isOA) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE),
    `Jan-2025` = sum(`Jan-2025`, na.rm = TRUE),
    `Feb-2025` = sum(`Feb-2025`, na.rm = TRUE),
    `Mar-2025` = sum(`Mar-2025`, na.rm = TRUE),
    `Apr-2025` = sum(`Apr-2025`, na.rm = TRUE),
    `May-2025` = sum(`May-2025`, na.rm = TRUE),
    `Jun-2025` = sum(`Jun-2025`, na.rm = TRUE)) |>
  ungroup() |>  
  mutate(Price = case_when(
    is.na(Price) == TRUE ~ utkMedPrice,
    .default = Price
  )) |>
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`,
         usage25 = `Jan-2025` + `Feb-2025` + `Mar-2025` + `Apr-2025` + `May-2025` + `Jun-2025`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24 + usage25) |>
  mutate(isCC22 = ifelse((YOP >= 2018 & YOP <= 2022) | YOP == 9999, 'Yes', 'No'),
         isCC23 = ifelse((YOP >= 2019 & YOP <= 2023) | YOP == 9999, 'Yes', 'No'),
         isCC24 = ifelse((YOP >= 2020 & YOP <= 2024) | YOP == 9999, 'Yes', 'No'),
         isCC25 = ifelse(YOP >= 2021, 'Yes', 'No')) |>
  mutate(isBackfile22 = ifelse(YOP > 1997 & YOP < 2018, 'Yes', 'No'),
         isBackfile23 = ifelse(YOP > 1997 & YOP < 2019, 'Yes', 'No'),
         isBackfile24 = ifelse(YOP > 1997 & YOP < 2020, 'Yes', 'No'),
         isBackfile25 = ifelse(YOP > 1997 & YOP < 2021, 'Yes', 'No')) |>
  mutate(isTrueBackfile = ifelse(YOP <= 1997, 'Yes', 'No')) |>
  mutate(currentYearUsage = case_when(
    YOP == 2022 ~ usage22,
    YOP == 2023 ~ usage23,
    YOP == 2024 ~ usage24,
    YOP == 2025 ~ usage25,
    .default = 0),
         ccClearanceUsage = case_when(
           isCC22 == 'Yes' & isCC23 == 'No' & isCC24 == 'No' & isCC25 == 'No' ~ usage22,
           isCC22 == 'Yes' & isCC23 == 'Yes' & isCC24 == 'No' & isCC25 == 'No' ~ usage22 + usage23,
           isCC22 == 'Yes' & isCC23 == 'Yes' & isCC24 == 'Yes' & isCC25 == 'No' ~ usage22 + usage23 + usage24,
           isCC22 == 'Yes' & isCC23 == 'Yes' & isCC24 == 'Yes' & isCC25 == 'Yes' ~ usage22 + usage23 + usage24 + usage25,
           isCC22 == 'No' & isCC23 == 'Yes' & isCC24 == 'Yes' & isCC25 == 'Yes' ~ usage23 + usage24 + usage25,
           isCC22 == 'No' & isCC23 == 'No' & isCC24 == 'Yes' & isCC25 == 'Yes' ~ usage24 + usage25,
           isCC22 == 'No' & isCC23 == 'No' & isCC24 == 'No' & isCC25 == 'Yes' ~ usage25,
           isCC22 == 'No' & isCC23 == 'No' & isCC24 == 'No' & isCC25 == 'No' ~ 0,
           .default = NA
         ),
        backfileUsage = case_when(
           isBackfile22 == 'Yes' & isBackfile23 == 'No' & isBackfile24 == 'No' & isBackfile25 == 'No' ~ usage22,
           isBackfile22 == 'Yes' & isBackfile23 == 'Yes' & isBackfile24 == 'No' & isBackfile25 == 'No' ~ usage22 + usage23,
           isBackfile22 == 'Yes' & isBackfile23 == 'Yes' & isBackfile24 == 'Yes' & isBackfile25 == 'No' ~ usage22 + usage23 + usage24,
           isBackfile22 == 'Yes' & isBackfile23 == 'Yes' & isBackfile24 == 'Yes' & isBackfile25 == 'Yes' ~ usage22 + usage23 + usage24 + usage25,
           isBackfile22 == 'No' & isBackfile23 == 'Yes' & isBackfile24 == 'Yes' & isBackfile25 == 'Yes' ~ usage23 + usage24 + usage25,
           isBackfile22 == 'No' & isBackfile23 == 'No' & isBackfile24 == 'Yes' & isBackfile25 == 'Yes' ~ usage24 + usage25,
           isBackfile22 == 'No' & isBackfile23 == 'No' & isBackfile24 == 'No' & isBackfile25 == 'Yes' ~ usage25,
           isBackfile22 == 'No' & isBackfile23 == 'No' & isBackfile24 == 'No' & isBackfile25 == 'No' ~ 0,
           .default = NA          
        ),
        trueBackFileUsage = ifelse(isTrueBackfile == 'Yes', Total_Usage, 0)
  )

TR_J4_Complete |>
  arrange(desc(ccClearanceUsage))
```






# TR_J1: Usage by Package Type and Individual Title Cost/Use



```{r}
TR_J1_Complete <- fullTR_J1 |>
  group_by(Title.x, Price, isOA) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE),
    `Jan-2025` = sum(`Jan-2025`, na.rm = TRUE),
    `Feb-2025` = sum(`Feb-2025`, na.rm = TRUE),
    `Mar-2025` = sum(`Mar-2025`, na.rm = TRUE),
    `Apr-2025` = sum(`Apr-2025`, na.rm = TRUE),
    `May-2025` = sum(`May-2025`, na.rm = TRUE),
    `Jun-2025` = sum(`Jun-2025`, na.rm = TRUE)) |>
  ungroup() |>
  mutate(Price = case_when(
    is.na(Price) == TRUE ~ utkMedPrice,
    .default = Price
  )) |>
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`,
         usage25 = `Jan-2025` + `Feb-2025` + `Mar-2025` + `Apr-2025` + `May-2025` + `Jun-2025`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24 + usage25) |>
  mutate(costUse = Price / (Total_Usage / 3.5))|>
  mutate(costUseBucket = case_when(
    isOA == 'Yes' ~ 'Full Open Access',
    costUse < 20 ~ 'Under $20',
    costUse >= 20 ~ 'Over $20'
  )
)

TR_J1_Complete
```


# TR_J3: Usage by OA Type, Including OA Titles



```{r}
TR_J3_Complete <- fullTR_J3 |>
  group_by(Title.x, Access_Type) |>
  summarise(`Jan-2022` = sum(`Jan-2022`, na.rm = TRUE),
    `Feb-2022` = sum(`Feb-2022`, na.rm = TRUE),
    `Mar-2022` = sum(`Mar-2022`, na.rm = TRUE),
    `Apr-2022` = sum(`Apr-2022`, na.rm = TRUE),
    `May-2022` = sum(`May-2022`, na.rm = TRUE),
    `Jun-2022` = sum(`Jun-2022`, na.rm = TRUE),
    `Jul-2022` = sum(`Jul-2022`, na.rm = TRUE),
    `Aug-2022` = sum(`Aug-2022`, na.rm = TRUE),
    `Sep-2022` = sum(`Sep-2022`, na.rm = TRUE),
    `Oct-2022` = sum(`Oct-2022`, na.rm = TRUE),
    `Nov-2022` = sum(`Nov-2022`, na.rm = TRUE),
    `Dec-2022` = sum(`Dec-2022`, na.rm = TRUE),
    `Jan-2023` = sum(`Jan-2023`, na.rm = TRUE),
    `Feb-2023` = sum(`Feb-2023`, na.rm = TRUE),
    `Mar-2023` = sum(`Mar-2023`, na.rm = TRUE),
    `Apr-2023` = sum(`Apr-2023`, na.rm = TRUE),
    `May-2023` = sum(`May-2023`, na.rm = TRUE),
    `Jun-2023` = sum(`Jun-2023`, na.rm = TRUE),
    `Jul-2023` = sum(`Jul-2023`, na.rm = TRUE),
    `Aug-2023` = sum(`Aug-2023`, na.rm = TRUE),
    `Sep-2023` = sum(`Sep-2023`, na.rm = TRUE),
    `Oct-2023` = sum(`Oct-2023`, na.rm = TRUE),
    `Nov-2023` = sum(`Nov-2023`, na.rm = TRUE),
    `Dec-2023` = sum(`Dec-2023`, na.rm = TRUE),
    `Jan-2024` = sum(`Jan-2024`, na.rm = TRUE),
    `Feb-2024` = sum(`Feb-2024`, na.rm = TRUE),
    `Mar-2024` = sum(`Mar-2024`, na.rm = TRUE),
    `Apr-2024` = sum(`Apr-2024`, na.rm = TRUE),
    `May-2024` = sum(`May-2024`, na.rm = TRUE),
    `Jun-2024` = sum(`Jun-2024`, na.rm = TRUE),
    `Jul-2024` = sum(`Jul-2024`, na.rm = TRUE),
    `Aug-2024` = sum(`Aug-2024`, na.rm = TRUE),
    `Sep-2024` = sum(`Sep-2024`, na.rm = TRUE),
    `Oct-2024` = sum(`Oct-2024`, na.rm = TRUE),
    `Nov-2024` = sum(`Nov-2024`, na.rm = TRUE),
    `Dec-2024` = sum(`Dec-2024`, na.rm = TRUE),
    `Jan-2025` = sum(`Jan-2025`, na.rm = TRUE),
    `Feb-2025` = sum(`Feb-2025`, na.rm = TRUE),
    `Mar-2025` = sum(`Mar-2025`, na.rm = TRUE),
    `Apr-2025` = sum(`Apr-2025`, na.rm = TRUE),
    `May-2025` = sum(`May-2025`, na.rm = TRUE),
    `Jun-2025` = sum(`Jun-2025`, na.rm = TRUE)) |>
  ungroup() |>
  mutate(usage22 = `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
         usage23 = `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
         usage24 = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`,
         usage25 = `Jan-2025` + `Feb-2025` + `Mar-2025` + `Apr-2025` + `May-2025` + `Jun-2025`) |>
  mutate(Total_Usage = usage22 + usage23 + usage24 + usage25)

TR_J3_Complete
```



# Add the Cost/Use Bucket and the Price from TR_Complete to TR_J4_Complete



```{r, warning = FALSE}
smallTRComplete <- TR_J1_Complete |>
  select(Title.x, costUseBucket, Price, isOA)

TR_J4_Export <- left_join(TR_J4_Complete, smallTRComplete, by = c('Title.x' = 'Title.x', 'Price' = 'Price', 'isOA' = 'isOA'))
```


# Create the Copyright Clearance Bucket Column


```{r}
TR_J4_Buckets <- TR_J4_Export |>
  group_by(Title.x, Price, isOA) |>
  summarise(copyrightClearanceUsage = sum(ccClearanceUsage)) |>
  mutate(ccCostUse = Price / (copyrightClearanceUsage / 3.5)) |>
  mutate(ccCostUseBucket = case_when(
    isOA == 'Yes' ~ 'Full Open Access',
    ccCostUse < 20 ~ 'Under $20',
    ccCostUse >= 20 ~ 'Over $20'
  )) |>
  mutate(ccCostUse = ifelse(is.infinite(ccCostUse) == TRUE, 0, ccCostUse))
```

```{r}
TR_J4_Export_Mid <- left_join(TR_J4_Export, TR_J4_Buckets, by = c('Title.x' = 'Title.x', 'Price' = 'Price')) 
```


# Clean up the Cost/Use Buckets in TR_J4

```{r}
TR_J4_Export_Final <- TR_J4_Export_Mid |>
  mutate(costUseBucket = case_when(
    is.na(costUseBucket) == TRUE & (Price / (Total_Usage / 3.5)) > 20 ~ 'Over $20',
    is.na(costUseBucket) == TRUE & (Price / (Total_Usage / 3.5)) < 20 ~ 'Under $20',
    .default = costUseBucket
  ))
```


# Export the Data

```{r}
write_xlsx(TR_J4_Export_Final, 'Springer Usage by Year of Publishing.xlsx')
```


# TR_Complete: Cost/Use by Campus



## TR_Complete: Total Usage by Campus


```{r}
TR_Complete_Usage = TR_J1_Complete |>
  group_by() |>
  summarise(Titles = length(unique(Title.x)),
            Usage = sum(Total_Usage)) |>
  mutate(Location = 'UT Knoxville')

TR_Complete_Usage
```


## Compare Total Usage to the Total Cost


```{r}
costPerUseTotal <- inner_join(springerPrice, TR_Complete_Usage, by = 'Location') |>
  mutate(costUse = Price / (Usage / 3.5),
         costTitle = Price / Titles)

costPerUseTotal
```




```{r}
write_xlsx(costPerUseTotal, 'Springer Package Cost Per Use Summary.xlsx')
```



# Pivot Tables Longer for Line Graphs



```{r}
TR_Complete_Longer <- TR_J1_Complete |>
  pivot_longer(cols = contains('-'),
               names_to = 'Month',
               values_to = 'Usage')

write_xlsx(TR_Complete_Longer, 'Springer Title Use and Title Cost Per Use.xlsx')
```



```{r}
TR_Complete_Longer_3 <- TR_J3_Complete |>
  pivot_longer(cols = contains('-'),
               names_to = 'Month',
               values_to = 'Usage')

write_xlsx(TR_Complete_Longer_3, 'Springer Usage by Access Type and Title.xlsx')
```






